---
title: "Divorce Models"
output: html_document
---

```{r, echo=F, message=F, warning=F}
library(tidyverse)
library(haven)
library(sjmisc)
library(gridExtra)
library(sjPlot)
library(ggplot2)
library(ggpubr)


setwd("~/UPF PhD/Divorce/GGP/")
d <- readRDS("wave1_cleaned.rds")

d$long_mobility <- relevel(as.factor(d$long_mobility), ref = "immobile")
d$scandinavia <- relevel(as.factor(d$scandinavia), ref = "Scandinavia")

```

# Variable Descriptions:

DV = Divorce (binary)

IV = Long Mobility (5 categories)

1. Highly upwardly mobile (moves up 2 class levels)

2. Upwardly mobile (moves up 1 class level)

3. Immobile (ref.)

4. Downwardly mobile (moves down 1 class level)

5. Highly downwardly mobile (moves down 2 class levels)

Controls = Age, age squared, education: Degree (ref.), age at marriage, age at married squared, country groups: Scandinavia (ref.)

## Effect of Long Mobility (5 categories) on Divorce

```{r, echo=F, message=F, warning=F, fig.width=8, fig.height=5}

m1 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + scandinavia + agemarr_p1 + I(agemarr_p1^2), family = "binomial", data = filter(d, asex == 1), weights = aweight)
m2 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + scandinavia + agemarr_p1 + I(agemarr_p1^2), family = "binomial", data = filter(d, asex == 2), weights = aweight)

plot1 <- plot_model(m1, title = "Men", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'scandinaviaEastern EU' = "Eastern Europe",
    'scandinaviaWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    dur = "Duration"
  ))

plot2 <- plot_model(m2, title = "Women", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'scandinaviaEastern EU' = "Eastern Europe",
    'scandinaviaWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    dur = "Duration"
  ))
ggarrange(plot1, plot2, ncol = 2)



```

## Effect of Long Mobility (5 categories) on Divorce by Country Groups (MEN)

```{r echo=F, fig.width=8, message=FALSE, warning=FALSE, fig.width=12, fig.height=5}

m3 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) , family = "binomial", data = filter(d, asex==1 & scandinavia=="Western EU"), weights = aweight)

plot3 <- plot_model(m3, title = "Western Europe", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    dur = "Duration"
  ))

m4 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2), family = "binomial", data = filter(d, asex ==1 & scandinavia == "Eastern EU"), weights = aweight)

plot4 <- plot_model(m4, title = "Eastern Europe", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    relig = "Religiosity dummy",
    dur = "Duration"
  ))

m5 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2), family = "binomial", data = filter(d, asex ==1 & scandinavia == "Scandinavia"), weights = aweight)

plot5 <- plot_model(m5, title = "Scandinavia", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    relig = "Religiosity dummy",
    dur = "Duration"
  ))


ggarrange(plot3, plot4, plot5, ncol = 3)

```

## Effect of Long Mobility (5 categories) on Divorce by Country Groups (WOMEN)

```{r echo=F, fig.width=8, message=FALSE, warning=FALSE, fig.width=12, fig.height=5}

m6 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2), family = "binomial", data = filter(d, asex==2 & scandinavia=="Western EU"), weights = aweight)

plot6 <- plot_model(m6, title = "Western Europe", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    dur = "Duration"
  ))

m7 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2), family = "binomial", data = filter(d, asex ==2 & scandinavia == "Eastern EU"), weights = aweight)

plot7 <- plot_model(m7, title = "Eastern Europe", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    relig = "Religiosity dummy",
    dur = "Duration"
  ))

m8 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2), family = "binomial", data = filter(d, asex ==2 & scandinavia == "Scandinavia"), weights = aweight)

plot8 <- plot_model(m8, title = "Scandinavia", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    relig = "Religiosity dummy",
    dur = "Duration"
  ))


ggarrange(plot6, plot7, plot8, ncol = 3)

```


# Inclusion of the duration of partnership that ended in divorce.

_The inclusion reduces the sample size_

## Effect of Social Mobility (Long) on Divorce

```{r, echo=F, message=F, warning=F, fig.width=8, fig.height=5}

m1 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + scandinavia + agemarr_p1 + I(agemarr_p1^2) + dur, family = "binomial", data = filter(d, asex == 1), weights = aweight)
m2 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + scandinavia + agemarr_p1 + I(agemarr_p1^2) + dur, family = "binomial", data = filter(d, asex == 2), weights = aweight)

plot1 <- plot_model(m1, title = "Men", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'scandinaviaEastern EU' = "Eastern Europe",
    'scandinaviaWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    dur = "Duration"
  ))

plot2 <- plot_model(m2, title = "Women", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'scandinaviaEastern EU' = "Eastern Europe",
    'scandinaviaWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    dur = "Duration"
  ))
ggarrange(plot1, plot2, ncol = 2)



```

## Effect of Long Mobility (5 categories) on Divorce by Country Groups (MEN)

```{r echo=F, fig.width=8, message=FALSE, warning=FALSE, fig.width=12, fig.height=5}

m3 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur, family = "binomial", data = filter(d, asex==1 & scandinavia=="Western EU"), weights = aweight)

plot3 <- plot_model(m3, title = "Western Europe", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    dur = "Duration"
  ))

m4 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur, family = "binomial", data = filter(d, asex ==1 & scandinavia == "Eastern EU"), weights = aweight)

plot4 <- plot_model(m4, title = "Eastern Europe", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    relig = "Religiosity dummy",
    dur = "Duration"
  ))

m5 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur, family = "binomial", data = filter(d, asex ==1 & scandinavia == "Scandinavia"), weights = aweight)

plot5 <- plot_model(m5, title = "Scandinavia", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    relig = "Religiosity dummy",
    dur = "Duration"
  ))


ggarrange(plot3, plot4, plot5, ncol = 3)

```

## Effect of Long Mobility (5 categories) on Divorce by Country Groups (WOMEN)

```{r echo=F, fig.width=8, message=FALSE, warning=FALSE, fig.width=12, fig.height=5}

m6 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur, family = "binomial", data = filter(d, asex==2 & scandinavia=="Western EU"), weights = aweight)

plot6 <- plot_model(m6, title = "Western Europe", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    dur = "Duration"
  ))

m7 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur, family = "binomial", data = filter(d, asex ==2 & scandinavia == "Eastern EU"), weights = aweight)

plot7 <- plot_model(m7, title = "Eastern Europe", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    relig = "Religiosity dummy",
    dur = "Duration"
  ))

m8 <- glm(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur, family = "binomial", data = filter(d, asex ==2 & scandinavia == "Scandinavia"), weights = aweight)

plot8 <- plot_model(m8, title = "Scandinavia", show.values = TRUE, value.offset = .3) +
  scale_y_continuous(limits = c(0.0001, 3)) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    relig = "Religiosity dummy",
    dur = "Duration"
  ))


ggarrange(plot6, plot7, plot8, ncol = 3)

```
