---
title: "Divorce Models"
output: html_document
---

```{r, echo=F, message=F, warning=F}
library(tidyverse)
library(haven)
library(sjmisc)
library(gridExtra)
library(sjPlot)
library(ggplot2)
library(ggpubr)
library(lme4)


setwd("~/UPF PhD/Divorce/GGP/")
d <- readRDS("wave1_cleaned.rds")

d$long_mobility <- relevel(as.factor(d$long_mobility), ref = "immobile")
d$scandinavia <- relevel(as.factor(d$scandinavia), ref = "Scandinavia")


```

## Effect of Long Mobility (5 categories) on Divorce

DV = Divorce (binary)

IV = Long Mobility (5 categories)

Controls = Age, age squared, education (3 levels), eastern dummy, age at marriage, age at married squared

1. Highly upwardly mobile (moves up 2 class levels)

2. Upwardly mobile (moves up 1 class level)

3. Immobile (ref.)

4. Downwardly mobile (moves down 1 class level)

5. Highly downwardly mobile (moves down 2 class levels)

```{r, echo=F, message=F, warning=F }

m1 <- glmer(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur +  (1 | country), data = filter(d, asex == 1), weights = aweight, family = "binomial")

m2 <- glmer(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur +  (1 | country), data = filter(d, asex == 2), weights = aweight, family = "binomial")

plot1 <- plot_model(m1, title = "Men", show.values = TRUE, value.offset = .3) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    dur = "Duration"
  ))

plot2 <- plot_model(m2, title = "Women", show.values = TRUE, value.offset = .3) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared", 
    dur = "Duration"
  ))
ggarrange(plot1, plot2, ncol = 2)


```

## Effect of Long Mobility (5 categories) on Divorce by Sex by Country

### Men

```{r, echo=F, message=F, warning=F, fig.width=10, fig.height=5}

m3 <- glmer(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur + (1 | country), family = "binomial", data = filter(d, asex==1 & scandinavia=="Western EU"), weights = aweight)

m4 <- glmer(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur + (1 | country), family = "binomial", data = filter(d, asex==1 & scandinavia=="Eastern EU"), weights = aweight)

m5 <- glmer(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur + (1 | country), family = "binomial", data = filter(d, asex==1 & scandinavia=="Scandinavia"), weights = aweight)

plot3 <- plot_model(m3, title = "Western Europe", show.values = TRUE, value.offset = .3) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    dur = "Duration"
  ))

plot4 <- plot_model(m4, title = "Eastern Europe", show.values = TRUE, value.offset = .3) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    relig = "Religiosity dummy",
    dur = "Duration"
  ))

plot5 <- plot_model(m4, title = "Scandinavia", show.values = TRUE, value.offset = .3) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    relig = "Religiosity dummy",
    dur = "Duration"
  ))

ggarrange(plot3, plot4, plot5, ncol = 3 )

```


### Women

```{r, echo=F, message=F, warning=F, fig.width=10, fig.height=5}

m6 <- glmer(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur + (1 | country), family = "binomial", data = filter(d, asex==2 & scandinavia=="Western EU"), weights = aweight)

m7 <- glmer(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur + (1 | country), family = "binomial", data = filter(d, asex==2 & scandinavia=="Eastern EU"), weights = aweight)

m8 <- glmer(divorce ~ long_mobility + aage + I(aage^2) + edu + agemarr_p1 + I(agemarr_p1^2) + dur + (1 | country), family = "binomial", data = filter(d, asex==2 & scandinavia=="Scandinavia"), weights = aweight)

plot6 <- plot_model(m6, title = "Western Europe", show.values = TRUE, value.offset = .3) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    dur = "Duration"
  ))

plot7 <- plot_model(m7, title = "Eastern Europe", show.values = TRUE, value.offset = .3) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    relig = "Religiosity dummy",
    dur = "Duration"
  ))

plot8 <- plot_model(m8, title = "Scandinavia", show.values = TRUE, value.offset = .3) +
  scale_x_discrete(labels = list(
    long_mobilitydownward = "Downwardly mobile",
    'long_mobilityhighly downward' = "Highly downwardly mobile",
    'long_mobilityhighly upward' = "Highly upwardly mobile",
    long_mobilityupward = "Upwardly mobile",
    aage = "Age",
    'I(aage^2)' = "Age squared",
    'edupost-secondary or tertiary' = "Edu: Post-seconary or Tertiary",
    'eduupper secondary' = "Edu: Upper secondary",
    'eastWestern EU' = "Western Europe",
    agemarr_p1 = "Age at first marriage",
    'I(agemarr_p1^2)' = "Age at first marraige squared",
    relig = "Religiosity dummy",
    dur = "Duration"
  ))

ggarrange(plot6, plot7, plot8, ncol = 3)

```


