---
title: "Job Tenure Over Time"
author: "Kimberly Seung Goulart"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r, echo=F, message=F, warning=F}

library(tidyverse)
library(haven)
library(beepr)
library(sjmisc)
library(ggpubr)
library(ggplot2)
library(plotly)
library(sjPlot)

setwd("/Volumes/GoogleDrive/My Drive/Thesis/Paper3/data")
five <- readRDS("5cleaned.rds")


```


# five Countries - UK, FR, DE, IT (includes the 4 Western European countries with the largest populations)

## Average Tenure Over Time 

I used both weights and multiplied them together - Post-stratification x Country In-Work population

```{r, echo=FALSE, message=FALSE, warning=FALSE}

countrytable <- five %>%
  group_by(country,year) %>%
  summarise(meantenure = weighted.mean(tenure, w5, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>%
  na.omit()

alltable <- five %>% 
  group_by(year) %>% 
  summarise(meantenure = weighted.mean(tenure, w5, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>% 
  mutate(country = "All") %>% 
  ungroup()

countrytable <- countrytable %>% 
  bind_rows(alltable)

ggplot(countrytable, aes(year,meantenure)) + 
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin=meantenure-se, ymax=meantenure+se), width=.2, position=position_dodge(0.05)) +
  labs(x = "Year", y = "Weighted Average Tenure") +
  facet_wrap(~country)

```


## Average Tenure Over Time by Gender

```{r, echo=FALSE, message=FALSE, warning=FALSE}

gendertable <- five %>%
  group_by(country,sex,year) %>%
  summarise(meantenure = weighted.mean(tenure, w5, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>%
  na.omit()

alltable <-five %>% 
  group_by(sex, year) %>% 
  summarise(meantenure = weighted.mean(tenure, w5, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>% 
  na.omit() %>% 
  mutate(country = "All") %>% 
  ungroup()

gendertable <- gendertable %>% 
  bind_rows(alltable)

ggplot(gendertable, aes(year,meantenure, group = sex, colour = sex)) + 
  geom_line() + 
  geom_point() +
  geom_errorbar(aes(ymin=meantenure-se, ymax=meantenure+se), width=.2, position=position_dodge(0.05)) +
  labs(x = "Year", y = "Weighted Average Tenure") +
  facet_wrap(~country)

```


## Average Tenure Over Time by Occupational Class

```{r, echo=FALSE, message=FALSE, warning=FALSE}

occtable <- five %>%
  group_by(country,occ_class,year) %>%
  summarise(meantenure = weighted.mean(tenure, w5, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>%
  na.omit()

alltable <-five %>% 
  group_by(occ_class, year) %>% 
  summarise(meantenure = weighted.mean(tenure, w5, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>% 
  na.omit() %>% 
  mutate(country = "All") %>% 
  ungroup()

occtable <- occtable %>% 
  bind_rows(alltable)

ggplot(occtable, aes(year,meantenure, group = occ_class, colour = occ_class)) + 
  geom_line() + 
  geom_point() +
  geom_errorbar(aes(ymin=meantenure-se, ymax=meantenure+se), width=.2, position=position_dodge(0.05)) +
  labs(x = "Year", y = "Weighted Average Tenure") +
  facet_wrap(~country)



```




## Models

Time (year) variable is treated as a continuous variable.

**Controls**
Age, age squared, migrant dummy, country

Weights - post-stratification weights
```{r, echo=FALSE, message=FALSE, warning=FALSE}

theme_set(theme_sjplot())

#five <- fastDummies::dummy_columns(five, select_columns = "occ_class")

# removes country dummies and includes workforce weight

summary(m1 <- lm(tenure ~ year + age + sex + imm, data = five, weights = w5))
m1plot <- plot_model(m1, type = 'pred', terms = c("year"), title = "All") + ylim(8, 15)

# m1 <- loess(tenure ~ year + age + women, data = five, weights = w5, span = 0.75)
# tibble(year = c(min(five$year):max(five$year)), age = mean(five$age), women = mean(five$women, na.rm = T)) %>% mutate(pred = predict(m1,.))
# 
# m1plot <- plot_model(m1, type = 'pred', terms = c("year"), title = "All") + ylim(8, 15)

summary(mfr <- lm(tenure ~ year + age + sex + imm + occ_class, data = filter(five, country=="FR"), weights = w4))
frplot <- plot_model(mfr, type = 'pred', terms = c("year"), title = "FR") + ylim(8, 15)

summary(mde <- lm(tenure ~ year + age + sex + imm + occ_class, data = filter(five, country=="DE"), weights = w4))
deplot <- plot_model(mde, type = 'pred', terms = c("year"), title = "DE") + ylim(8, 15)

summary(mit <- lm(tenure ~ year + age + sex + imm + occ_class, data = filter(five, country=="IT"), weights = w4))
itplot <- plot_model(mit, type = 'pred', terms = c("year"), title = "IT") + ylim(08, 15)

summary(mes <- lm(tenure ~ year + age + sex + imm + occ_class, data = filter(five, country=="ES"), weights = w4))
esplot <- plot_model(mes, type = 'pred', terms = c("year"), title = "ES") + ylim(8, 15)

summary(muk <- lm(tenure ~ year + age + sex + imm + occ_class, data = filter(five, country=="UK"), weights = w4))
ukplot <- plot_model(muk, type = 'pred', terms = c("year"), title = "UK") + ylim(8, 15)

ggarrange(frplot, deplot, itplot, esplot, ukplot, m1plot)



```

```{r}
mall1 <- lm(tenure ~ year*sex + age + + imm + occ_class, data = filter(five), weights = w5)
mall1plot <- plot_model(mall1, type = "pred", terms = c("year", "sex"))

mfr1 <- lm(tenure ~ year*sex + age + + imm + occ_class, data = filter(five, country=="FR"), weights = w4)
fr1plot <- plot_model(mfr1, type = "pred", terms = c("year", "sex"))

mde1 <- lm(tenure ~ year*sex + age + + imm + occ_class, data = filter(five, country=="DE"), weights = w4)
de1plot <- plot_model(mde1, type = "pred", terms = c("year", "sex"))

mit1 <- lm(tenure ~ year*sex + age + + imm + occ_class, data = filter(five, country=="IT"), weights = w4)
mit1plot <- plot_model(mit1, type = "pred", terms = c("year", "sex"))

mes1 <- lm(tenure ~ year*sex + age + + imm + occ_class, data = filter(five, country=="ES"), weights = w4)
mes1plot <- plot_model(mes1, type = "pred", terms = c("year", "sex"))

muk1 <- lm(tenure ~ year*sex + age + + imm + occ_class, data = filter(five, country=="UK"), weights = w4)
muk1plot <- plot_model(muk1, type = "pred", terms = c("year", "sex"))

ggarrange(fr1plot, de1plot, mit1plot, mes1plot, muk1plot, mall1plot)



```




### Interactions

```{r}

summary(m2 <- lm(tenure ~ year*country + age + sex + imm + occ_class, data = five, weights = w4))
plot_model(m2, type = "pred", terms = c("year", "country"))

summary(m3 <- lm(tenure ~ year*sex*country + age + imm + occ_class, data = five, weights = w4))
plot_model(m3, type = "pred", terms = c("year", "sex", "country"))

summary(m4 <- lm(tenure ~ year*occ_class + age + imm + occ_class, data = five, weights = w4))
plot_model(m4, type = "pred", terms = c("year", "occ_class"))

summary(m5 <- lm(tenure ~ year*occ_class*country + age + imm + occ_class, data = five, weights = w4))
plot_model(m5, type = "pred", terms = c("year", "occ_class", "country"))


```




### Testing to see how well the model worked.

```{r}
five <-five %>% 
  mutate(pred = predict(m1, newdata = .))

five %>% select(tenure, pred) %>% pivot_longer(cols = everything()) %>% ggplot(aes(value, fill = name)) + geom_density(alpha = .5)

```