---
title: "Job Tenure Over Time"
author: "Kimberly Seung Goulart"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r, echo=F, message=F, warning=F}

library(tidyverse)
library(haven)
library(beepr)
library(sjmisc)
library(ggpubr)
library(ggplot2)
library(plotly)
library(sjPlot)

setwd("/Volumes/GoogleDrive/My Drive/Thesis/Paper3/data")
five <- readRDS("5cleaned.rds")


```


# Five Countries - UK, FR, DE, IT, and ES 

**Poland was not included because it only entered the sample in 2000**

## Average Tenure Over Time 

**Only in-work population weights are used.**

```{r, echo=FALSE, message=FALSE, warning=FALSE}

countrytable <- five %>%
  group_by(country,year) %>%
  summarise(meantenure = weighted.mean(tenure, w5, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>%
  na.omit()

alltable <- five %>% 
  group_by(year) %>% 
  summarise(meantenure = weighted.mean(tenure, w5, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>% 
  mutate(country = "All") %>% 
  ungroup()

countrytable <- countrytable %>% 
  bind_rows(alltable)

ggplot(countrytable, aes(year,meantenure)) + 
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin=meantenure-se, ymax=meantenure+se), width=.2, position=position_dodge(0.05)) +
  labs(x = "Year", y = "Weighted Average Tenure") +
  facet_wrap(~country)

```


## Average Tenure Over Time by Gender

```{r, echo=FALSE, message=FALSE, warning=FALSE}

gendertable <- five %>%
  group_by(country,sex,year) %>%
  summarise(meantenure = weighted.mean(tenure, w5, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>%
  na.omit()

alltable <-five %>% 
  group_by(sex, year) %>% 
  summarise(meantenure = weighted.mean(tenure, w5, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>% 
  na.omit() %>% 
  mutate(country = "All") %>% 
  ungroup()

gendertable <- gendertable %>% 
  bind_rows(alltable)

ggplot(gendertable, aes(year,meantenure, group = sex, colour = sex)) + 
  geom_line() + 
  geom_point() +
  geom_errorbar(aes(ymin=meantenure-se, ymax=meantenure+se), width=.2, position=position_dodge(0.05)) +
  labs(x = "Year", y = "Weighted Average Tenure") +
  facet_wrap(~country)

```


## Average Tenure Over Time by Occupational Class

```{r, echo=FALSE, message=FALSE, warning=FALSE}

occtable <- five %>%
  group_by(country,occ_class,year) %>%
  summarise(meantenure = weighted.mean(tenure, w5, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>%
  na.omit()

alltable <-five %>% 
  group_by(occ_class, year) %>% 
  summarise(meantenure = weighted.mean(tenure, w5, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>% 
  na.omit() %>% 
  mutate(country = "All") %>% 
  ungroup()

occtable <- occtable %>% 
  bind_rows(alltable)

ggplot(occtable, aes(year,meantenure, group = occ_class, colour = occ_class)) + 
  geom_line() + 
  geom_point() +
  geom_errorbar(aes(ymin=meantenure-se, ymax=meantenure+se), width=.2, position=position_dodge(0.05)) +
  labs(x = "Year", y = "Weighted Average Tenure") +
  facet_wrap(~country)



```




## Models

### Effect of Year on Tenure

Time (year) variable is treated as a continuous variable.

**Controls**
Age, age squared, migrant dummy, occupational classes

**Weights**
Only used post-stratification weights

```{r, echo=FALSE, message=FALSE, warning=FALSE}

theme_set(theme_sjplot())

m1 <- lm(tenure ~ year + age + sex + imm, data = five, weights = w5)
m1plot <- plot_model(m1, type = 'pred', terms = c("year"), title = "All") + ylim(8, 15)

fr1 <- lm(tenure ~ year + age + sex + imm + occ_class, data = filter(five, country=="FR"), weights = w4)
fr1plot <- plot_model(fr1, type = 'pred', terms = c("year"), title = "FR") + ylim(7, 15)

de1 <- lm(tenure ~ year + age + sex + imm + occ_class, data = filter(five, country=="DE"), weights = w4)
de1plot <- plot_model(de1, type = 'pred', terms = c("year"), title = "DE") + ylim(7, 15)

it1 <- lm(tenure ~ year + age + sex + imm + occ_class, data = filter(five, country=="IT"), weights = w4)
it1plot <- plot_model(it1, type = 'pred', terms = c("year"), title = "IT") + ylim(7, 15)

es1 <- lm(tenure ~ year + age + sex + imm + occ_class, data = filter(five, country=="ES"), weights = w4)
es1plot <- plot_model(es1, type = 'pred', terms = c("year"), title = "ES") + ylim(7, 15)

uk1 <- lm(tenure ~ year + age + sex + imm + occ_class, data = filter(five, country=="UK"), weights = w4)
uk1plot <- plot_model(uk1, type = 'pred', terms = c("year"), title = "UK") + ylim(7, 15)

ggarrange(fr1plot, de1plot, it1plot, es1plot, uk1plot, m1plot,
          common.legend = TRUE)



```


### Effect of Year on Tenure by Gender

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}

m2 <- lm(tenure ~ year*sex + age + imm + occ_class, data = filter(five), weights = w5)
m2plot <- plot_model(m2, type = "pred", terms = c("year", "sex"), title = "All") + ylim(7, 14)

fr2 <- lm(tenure ~ year*sex + age + imm + occ_class, data = filter(five, country=="FR"), weights = w4)
fr2plot <- plot_model(fr2, type = "pred", terms = c("year", "sex"), title = "FR") + ylim(7, 14)

de2 <- lm(tenure ~ year*sex + age + imm + occ_class, data = filter(five, country=="DE"), weights = w4)
de2plot <- plot_model(de2, type = "pred", terms = c("year", "sex"), title = "DE") + ylim(7, 14)

it2 <- lm(tenure ~ year*sex + age + imm + occ_class, data = filter(five, country=="IT"), weights = w4)
it2plot <- plot_model(it2, type = "pred", terms = c("year", "sex"), title = "IT") + ylim(7, 14)

es2 <- lm(tenure ~ year*sex + age + imm + occ_class, data = filter(five, country=="ES"), weights = w4)
es2plot <- plot_model(es2, type = "pred", terms = c("year", "sex"), title = "ES") + ylim(7, 14)

uk2 <- lm(tenure ~ year*sex + age + imm + occ_class, data = filter(five, country=="UK"), weights = w4)
uk2plot <- plot_model(uk2, type = "pred", terms = c("year", "sex"), title = "UK") + ylim(7, 14)

ggarrange(fr2plot, de2plot, it2plot, es2plot, uk2plot, m2plot,
          common.legend = TRUE)



```


### Effect of Year on Tenure by Occupational Class

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}

m3 <- lm(tenure ~ year*occ_class + age + imm + sex, data = filter(five), weights = w5)
m3plot <- plot_model(m3, type = "pred", terms = c("year", "occ_class"), title = "All") + ylim(6, 15)

fr3 <- lm(tenure ~ year*occ_class + age + imm + sex, data = filter(five, country=="FR"), weights = w4)
fr3plot <- plot_model(fr3, type = "pred", terms = c("year", "occ_class"), title = "FR") + ylim(6, 15)

de3 <- lm(tenure ~ year*occ_class + age + imm + sex, data = filter(five, country=="DE"), weights = w4)
de3plot <- plot_model(de3, type = "pred", terms = c("year", "occ_class"), title = "DE") + ylim(6, 15)

it3 <- lm(tenure ~ year*occ_class + age + imm + sex, data = filter(five, country=="IT"), weights = w4)
it3plot <- plot_model(it3, type = "pred", terms = c("year", "occ_class"), title = "IT") + ylim(6, 15)

es3 <- lm(tenure ~ year*occ_class + age + imm + sex, data = filter(five, country=="ES"), weights = w4)
es3plot <- plot_model(es3, type = "pred", terms = c("year", "occ_class"), title = "ES") + ylim(6, 15)

uk3 <- lm(tenure ~ year*occ_class + age + imm + sex, data = filter(five, country=="UK"), weights = w4)
uk3plot <- plot_model(uk3, type = "pred", terms = c("year", "occ_class"), title = "UK") + ylim(6, 15)

ggarrange(fr3plot, de3plot, it3plot, es3plot, uk3plot, m3plot,
          common.legend = TRUE)

```

