---
title: "Job Tenure Over Time"
author: "Kimberly Seung Goulart"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r, echo=F, message=F, warning=F}

library(tidyverse)
library(haven)
library(beepr)
library(sjmisc)
library(ggpubr)
library(ggplot2)
library(plotly)
library(sjPlot)

setwd("/Volumes/GoogleDrive/My Drive/Thesis/Paper3/data")
four <- readRDS("4cleaned.rds")


```


# Four Countries - UK, FR, DE, IT (includes the 4 Western European countries with the largest populations)

## Average Tenure Over Time 

I used both weights and multiplied them together - Post-stratification x Country In-Work popoulation

```{r, echo=FALSE, message=FALSE, warning=FALSE}

countrytable <- four %>%
  group_by(country,year) %>%
  summarise(meantenure = weighted.mean(tenure, w45, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>%
  na.omit()

alltable <- four %>% 
  group_by(year) %>% 
  summarise(meantenure = weighted.mean(tenure, w45, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>% 
  mutate(country = "All") %>% 
  ungroup()

countrytable <- countrytable %>% 
  bind_rows(alltable)

ggplot(countrytable, aes(year,meantenure)) + 
  geom_line() + 
  geom_point() +
  geom_errorbar(aes(ymin=meantenure-se, ymax=meantenure+se), width=.2, position=position_dodge(0.05)) +
  labs(x = "Year", y = "Weighted Average Tenure") +
  facet_wrap(~country)

```


## Average Tenure Over Time by Gender

```{r, echo=FALSE, message=FALSE, warning=FALSE}

gendertable <- four %>%
  group_by(country,sex,year) %>%
  summarise(meantenure = weighted.mean(tenure, w45, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>%
  na.omit()

alltable <-four %>% 
  group_by(sex, year) %>% 
  summarise(meantenure = weighted.mean(tenure, w45, na.rm = T),
            count = n(),
            se = sd(tenure, na.rm = T)/sqrt(count)) %>% 
  na.omit() %>% 
  mutate(country = "All") %>% 
  ungroup()

gendertable <- gendertable %>% 
  bind_rows(alltable)

ggplot(gendertable, aes(year,meantenure, group = sex, colour = sex)) + 
  geom_line() + 
  geom_point() +
  geom_errorbar(aes(ymin=meantenure-se, ymax=meantenure+se), width=.2, position=position_dodge(0.05)) +
  labs(x = "Year", y = "Weighted Average Tenure") +
  facet_wrap(~country)



```


## Models

Time (year) variable is treated as a continuous variable.

**Controls**
Age, age squared, migrant dummy, country

Weights - post-stratification weights
```{r, echo=FALSE, message=FALSE, warning=FALSE}

theme_set(theme_sjplot())

summary(m1 <- lm(tenure ~ year + age + I(age^2) + sex + imm + country, data = four, weights = w45))
plot_model(m1, type = 'pred', terms = c("year"))

summary(m2 <- lm(tenure ~ year*country + age + I(age^2) + sex + imm + country, data = four, weights = w4))
plot_model(m2, type = "pred", terms = c("year", "country"))

summary(m3 <- lm(tenure ~ year*cohort*country + age + I(age^2) + sex + imm , data = four, weights = w4))
plot_model(m3, type = "pred", terms = c("year", "cohort", "country"))

summary(m4 <- lm(tenure ~ year*sex*country + age + I(age^2) + imm, data = four, weights = w4))
plot_model(m4, type = "pred", terms = c("year", "sex", "country"))



```


### Testing to see how well the model worked.

```{r}
four <-four %>% 
  mutate(pred = predict(m1, newdata = .))

four %>% select(tenure, pred) %>% pivot_longer(cols = everything()) %>% ggplot(aes(value, fill = name)) + geom_density(alpha = .5)

```